\section{Ambition and Impact}
It is the aim of DEIS to provide an efficient approach for assuring the dependability of smart cyber physical systems with a particular focus on assuring the safety of CPS including the impact of security on safety. As of today, there is no appropriate approach available to assure dependability of CPSs. Thus the results of DEIS will provide a significant innovation going clearly beyond the current state of the art.
In order to reach this ambitious goal, DEIS is built upon a single concept that can be applied throughout the complete product lifecycle from the creation of single components to the integration of systems and finally to the integration of decentralized CPSs in the field. To this end, DEIS starts by building on existing approaches, which are incrementally extended during the project. This seamless approach assures the practical applicability of the results by avoiding a technology break between development time dependability assurance on the one hand and in-the-field dependability assurance on the other hand. Moreover, this enables an evolutionary innovation from the current state-of-the-practice to the dependability assurance of CPS and thus improves the transferability of the results. As a further important aspect, the resulting similarity of in-the-field dependability assurance to existing development time dependability assurance approaches improves the acceptance by safety assessors or certification bodies. This seamless coverage of the complete product lifecycle is a further innovation in its own right since existing approaches either focus on dependability assurance at development time or they provide unlinked runtime mechanisms, which can hardly be integrated into an overall dependability assurance lifecycle for CPSs.